---
title: "Automated extraction of NHP tagged-run params"
date: "last-modified"
date-format: D MMM YYYY HH:mm
format: html
---

```{r}
#| label: check-env-vars
#| results: "asis"
#| echo: false

required_env_vars <- c(
  "AZ_TENANT_ID",
  "AZ_STORAGE_EP",
  "AZ_STORAGE_CONTAINER_RESULTS",
  "AZ_STORAGE_CONTAINER_SUPPORT",
  "NHP_ENCRYPT_KEY"
)
if (any(Sys.getenv(required_env_vars) == "")) {
  cat("One of the following environment variables was not set, so exiting \n\n")
  cat(paste("*", required_env_vars, collapse = "\n"), "\n\n")
  knitr::knit_exit() 
}
```

```{r}
#| label: setup
#| echo: false

source("R/azure.R")
source("R/pin.R")
```

## Purpose

A Quarto document deployed to Posit Connect that runs on schedule.
The source is in the [The-Strategy-Unit/nhp_tagged_runs_params](https://github.com/The-Strategy-Unit/nhp_tagged_runs_params) GitHub repo.

Generates and [pins](https://pins.rstudio.com/):

* a list object containing the model params for each NHP scheme's latest [tagged model run](https://connect.strategyunitwm.nhs.uk/nhp/tagged_runs)
* a data.frame object containing metadata associated with the tagged runs

The pins make it easier and faster to ingest params data into products like [the mitigators-comparison app](https://github.com/The-Strategy-Unit/nhp_inputs_report_app), for example.
This is a workaround because the results files are very large but certain tasks only require the params component.
In future, the params and results files will be stored separately, reducing the need for this functionality.

## Products

You can access on Posit Connect (login- and permissions-dependent):

* the params pin at matt.dray/nhp_tagged_runs_params
* the metadata pin at matt.dray/nhp_tagged_runs_meta

## Code

The steps in this report are to:

1. Identify on Azure the latest tagged results files, via their 'run_stage' metadata.
1. Pin their metadata.
1. Read the corresponding results JSON files from Azure.
1. Extract only the params element of each file and add to a named list.
1. Pin the params.

The pins will not be updated if there is no new data.

### Boards

Try to connect to the pin boards on both servers (both are active in May 2025, though the new board will become the main one and eventually take the name of the old server).

```{r}
#| label: board-connect

possibly_connect <- purrr::possibly(pins::board_connect)  # NULL on failure

board <- possibly_connect(server = "connect.strategyunitwm.nhs.uk")
board_new <- possibly_connect(server = "connect.su.mlcsu.org")
```

### Metadata

#### Data

Files are stored in two separate containers: one with results, one with supporting information.

```{r}
#| label: get-containers

container_results <-
  get_container(container_name = Sys.getenv("AZ_STORAGE_CONTAINER_RESULTS"))

container_support <-
  get_container(container_name = Sys.getenv("AZ_STORAGE_CONTAINER_SUPPORT"))
```

Read the metadata for the runs that are available and then isolate the ones tagged as 'final'. If no final run is found, choose the one labelled 'intermediate', otherwise 'initial'. Non-demographic growth (NDG) variant 2 is preferred.

```{r}
#| label: get-meta

meta <- fetch_tagged_runs_meta(container_results, container_support)
knitr::kable(meta)
```

#### Pin

Pin this metadata to both servers (if possible, depending on board availability). The `pin_if_board_exists()` function will only write the pin if a connection to the board has been successful.

```{r}
#| label: pin-meta
 
pin_if_board_exists(board, meta, "matt.dray/nhp_tagged_runs_meta")
pin_if_board_exists(board_new, meta, "matt.dray/nhp_tagged_runs_meta")
```

### Params

#### Data

Given the metadata, read the corresponding `file` for each model run.

```{r}
#| label: get-params

params_list <- fetch_tagged_runs_params(meta, container_results)
names(params_list)
```

#### Pin

Pin the params (if possible, depending on board availability).

```{r}
#| label: pin-params

pin_if_board_exists(board, params_list, "matt.dray/nhp_tagged_runs_params")
pin_if_board_exists(board_new, params_list, "matt.dray/nhp_tagged_runs_params")
```
