---
title: "Automated extraction of NHP tagged-run params"
date: "last-modified"
date-format: D MMM YYYY HH:mm
format: html
---

```{r}
#| label: check-env-vars
#| results: "asis"
#| echo: false

required_env_vars <- c(
  "AZ_TENANT_ID",
  "AZ_STORAGE_EP",
  "AZ_STORAGE_CONTAINER_RESULTS",
  "AZ_STORAGE_CONTAINER_SUPPORT",
  "NHP_ENCRYPT_KEY"
)
if (any(Sys.getenv(required_env_vars) == "")) {
  cat("One of the following environment variables was not set, so exiting \n\n")
  cat(paste("*", required_env_vars, collapse = "\n"), "\n\n")
  knitr::knit_exit() 
}
```

```{r}
#| label: setup
#| echo: false

source("R/azure.R")
```

## Purpose

A Quarto document deployed to Post Connect that runs on schedule.

Generates and [pins](https://pins.rstudio.com/) a list containing the model params for each NHP scheme's latest [tagged run](https://connect.strategyunitwm.nhs.uk/nhp/tagged_runs).

This makes it easier and faster to ingest params data into products like the mitigators-comparison app, for example.

The pinned object can be [accessed on Posit Connect](https://connect.strategyunitwm.nhs.uk/content/32c7f642-e420-448d-b888-bf655fc8fa8b/) if you have sufficient permissions.

## Code

The steps are to:

1. Identify the latest tagged runs.
1. Read the corresponding JSON files from Azure.
1. Extract only the params element and add to to a named list.
1. Write this object to a pin, ready for ingestion by other processes.

Files stored in two separate containers: one with results, one with supporting information.

```{r}
#| label: get-containers

container_results <-
  get_container(container_name = Sys.getenv("AZ_STORAGE_CONTAINER_RESULTS"))

container_support <-
  get_container(container_name = Sys.getenv("AZ_STORAGE_CONTAINER_SUPPORT"))
```

Read the metadata for the runs that are available and then isolate the ones tagged as 'final'. If no final run is found, choose the one labelled 'intermediate', otherwise 'initial'. Non-demographic growth (NDG) variant 2 is preferred.

```{r}
#| label: get-meta

runs_meta <- fetch_tagged_runs_meta(container_results, container_support)
knitr::kable(runs_meta)
```

Given the metadata, read the corresponding `file` for each model run.

```{r}
#| label: get-params

params_list <- fetch_tagged_runs_params(runs_meta, container_results)
names(params_list)
```

Write to [the pin](https://connect.strategyunitwm.nhs.uk/content/32c7f642-e420-448d-b888-bf655fc8fa8b/).

```{r}
#| label: pin-data

board <- pins::board_connect()

pins::pin_write(
  board,
  x = params_list,
  name = "matt.dray/nhp_tagged_runs_params", 
  type = "rds",
  title = "NHP tagged-run params",
  description = "Params from schemes' latest tagged model runs.",
  versioned = TRUE
)
```

The pin will not be overwritten if there hasn't been a change to the tagged runs.
